Kids Moisture Summary

### 2020-01-16 home_char_act_cleaning.Rmd
cleaning and summary stat updates

---
title: "KidsAIR home activity and characteristics cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 13 Jan 2020"
output: pdf_document
---

@@

# Clean up all home characteristics data
```{r}
kids_home_char <- read_rds("Output/kids_home_char.rds")

kids_home_char_clean <- kids_home_char

# write_rds(kids_home_char_clean, "Output/kids_home_char_clean.rds")
```

@@

# Clean up all home activity data
```{r}
kids_home_act <- read_rds("Output/kids_home_act.rds")

kids_home_act_clean <- kids_home_act

# write_rds(kids_home_act_clean, "Output/kids_home_act_clean.rds")
```

>>>>

---
title: "KidsAIR home activity and characteristics cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 15 Jan 2020"
output: pdf_document
---

@@

# Clean up all home characteristics data
```{r}
kids_home_char <- read_rds("Output/kids_home_char.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")

home_char_clean <- kids_home_char %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))

# write_rds(home_char_clean, "Output/home_char_clean.rds")
```

@@

# Clean up all home activity data
```{r}
kids_home_act <- read_rds("Output/kids_home_act.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")

home_act_clean <- kids_home_act %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))

# write_rds(home_act_clean, "Output/home_act_clean.rds")
```

### 2020-01-16 moisture_summary.Rmd
cleaning and summary stat updates

---
title: "Kids Moisture Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 14 Jan 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

# Summary stats
```{r}
summary_moisture <- moisture_clean %>% 
  group_by(area) %>% 
  summarize(mean(moisture_ave, na.rm = TRUE), sd(moisture_ave, na.rm = TRUE),
            median(moisture_ave, na.rm = TRUE),
            min(moisture_ave, na.rm = TRUE), max(moisture_ave, na.rm = TRUE)) %>% 
  t()
summary_moisture
```

>>>>

---
title: "Kids Moisture Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 15 Jan 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, 
                      include = TRUE, warning = FALSE)
```

@@

# Moisture content summary stats
## Average of 3 measurements
```{r}
summary_moisture <- moisture_clean %>%
  group_by(area) %>% 
  summarize(mean = mean(moisture_ave, na.rm = TRUE), 
            SD = sd(moisture_ave, na.rm = TRUE),
            median = median(moisture_ave, na.rm = TRUE),
            min = min(moisture_ave, na.rm = TRUE), 
            max = max(moisture_ave, na.rm = TRUE)) %>%
  select(-area) %>% 
  t() 
kable(summary_moisture, col.names = c("Alaska", "Navajo", "Montana"), 
      digits = 1, align = "c")
```

# Was wood split?
```{r}
wood_split <- moisture_clean %>% 
  filter(!is.na(moisture_split)) %>% 
  group_by(area, moisture_split) %>% 
  summarise(n = n())
kable(wood_split, align = "c")
```
